---
title: "Practical 4"
author: "Divij"
date: "8/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##  Histogram

```{r}
require(ggplot2)
str(diamonds)
hist(diamonds$carat, main="Carat Histogram", xlab="carat")
```

##  Scater Plot

```{r}
plot(price ~ carat, data = diamonds)
```

##  Box Plot

```{r}
boxplot(diamonds$carat)
```

##  ggPlot geom_histogram

```{r}
ggplot(data = diamonds) + geom_histogram(aes(x=carat))
```

##  ggPlot geom_density

```{r}
ggplot(data = diamonds) + geom_density(aes(x=carat),fill="grey50")
```

##  ggPlot geom_density

```{r}
ggplot(data = diamonds) + geom_density(aes(x=carat),fill="cyan")
```

##  ggPlot geom_density yellow

```{r}
ggplot(data = diamonds) + geom_density(aes(x=carat),fill="yellow")
```

##  ggPlot geom_point

```{r}
ggplot(diamonds, aes(x=carat, y=price)) + geom_point()
```

##  ggPlot geom_point color

```{r}
g <- ggplot(diamonds, aes(x=carat, y=price)) 
g + geom_point(aes(color=color))
```

##  ggPlot geom_point cut

```{r}
g <- ggplot(diamonds, aes(x=carat, y=price)) 
g + geom_point(aes(color=cut))
```

##  ggPlot geom_point clarity

```{r}
g <- ggplot(diamonds, aes(x=carat, y=price)) 
g + geom_point(aes(color=clarity))
```

##  ggPlot geom_point color facet_wrap color

```{r}
g <- ggplot(diamonds, aes(x=carat, y=price)) 
g + geom_point(aes(color=color)) + facet_wrap(~color)
```

##  ggPlot geom_point color facet_wrap cut

```{r}
g <- ggplot(diamonds, aes(x=carat, y=price)) 
g + geom_point(aes(color=color)) + facet_wrap(~cut)
```

##  ggPlot geom_point color facet_wrap clarity

```{r}
g <- ggplot(diamonds, aes(x=carat, y=price)) 
g + geom_point(aes(color=color)) + facet_wrap(~clarity)
```

##  ggPlot geom_point color facet_grid cut vs clarity

```{r}
g <- ggplot(diamonds, aes(x=carat, y=price)) 
g + geom_point(aes(color=color)) + facet_grid(cut ~ clarity)
```

##  ggPlot geom_boxplot

```{r}
ggplot(diamonds, aes(y=carat, x=cut)) + geom_boxplot()
```

##  ggPlot geom_violin

```{r}
ggplot(diamonds, aes(y=carat, x=cut)) + geom_violin()
```

##  ggPlot geom_boxplot

```{r}
ggplot(diamonds, aes(y=carat, x=cut, color=color)) + geom_boxplot()
```

##  ggPlot geom_point geom_boxplot

```{r}
ggplot(diamonds, aes(y=carat, x=cut)) + geom_point() + geom_boxplot()
```

##  ggPlot geom_boxplot geom_point

```{r}
ggplot(diamonds, aes(y=carat, x=cut)) + geom_boxplot() + geom_point()
```

##  ggPlot geom_point geom_violin

```{r}
ggplot(diamonds, aes(y=carat, x=cut)) + geom_point() + geom_violin()
```

##  ggPlot geom_violin geom_point

```{r}
ggplot(diamonds, aes(y=carat, x=cut)) + geom_violin() + geom_point()
```

##  ggPlot geom_line

```{r}
ggplot(economics, aes(y=date, x=pop)) + geom_line() 
```

##  ggPlot geom_line

```{r}
require(ggplot2)
require(ggthemes)

g2 <- ggplot(diamonds, aes(x=carat, y=price)) + geom_point(aes(color=color))

g2 + theme_economist() + scale_color_economist()
```
```{r}
x <- rnorm(200)
hist(x,main="Histogram",
     ylim=c(0,0.5),prob=TRUE)
lines(density(x),col="blue")
```
